---
title: "W_UP_01"
author: "Jared Lobitana"
date: "Summer 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

We are trying to find the average number of push ups between skill player and line and the players. Is there a statistical difference in the average number of push ups between both positions. 


$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

We will be using the numerical ~ categorical. Numerical for the number average of push ups and categorical for the different positions. The method I will use will be a box plot and we also will be using the numerical summary, lastly for the inferential test we will be using the t-test. 


# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
boxplot(pushups~position,data=mydata)
```

The box plot shows that the skill player position on average does around 60 push ups and the line position have less than 28 push ups.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

In this table summary we've found that the mean in the line player is about 17 and the skill player is about 50. The  difference in mean is around 33 push ups.


## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

The t-test show that there's a difference in average push ups between the line player and the skill player the p- value that we got is 0.000009421, the p-value is too small that's why we reject the null hypothesis the difference is 33 push ups more than line players. 95 percent of the time the skill player do.


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

To restate the question, who does more push ups on average position is it the line player or the skill player. We have found that there is a difference on push ups done per line player. The difference is 95 percent at the time that do 28 or 30 push ups at the time. The skills player do more push ups than the line player. The p-value is too small that leads us to reject the null hypothesis. We have found there is a statistical difference. 



